A tutorial of Solving the defined integral problem with OpenMp

### 2023-05-28 documentation/article.tex
Minor fixes

	\section{Performance tests}
		\par The tests were done using an \textit{AMD Ryzen 5 5000 series} running an \textit{Gnu/Linux operational system} with \textit{30GB of RAM}.\newline

>>>>

	\section{Performance tests}
		\par The tests were done using an \textit{AMD Ryzen 5 5000 series} processor running an \textit{Gnu/Linux operational system} with \textit{30GB of RAM}.\newline
